### 2018-03-16 paper.Rmd
recoloring color plot

count_estimates <- color_counts %>%
  mutate(age = target_child_age / 30.5,
         age_bin = as.integer(floor(age / 6) * 6),
         color = tolower(gloss)) %>%
  group_by(age_bin, color, target_child_id) %>%
  summarise(count = sum(count)) %>%
  summarise(mean = mean(count, na.rm = T),
            sem = sd(count, na.rm = T) / sqrt(sum(!is.na(count)))) %>%
  left_join(graph_colors)

>>>>

count_estimates <- color_counts %>%
  mutate(age = target_child_age / 30.5,
         age_bin = as.integer(floor(age / 6) * 6),
         color = tolower(gloss)) %>%
  group_by(age_bin, color, target_child_id) %>%
  summarise(count = sum(count)) %>%
  summarise(mean = mean(count, na.rm = T),
            sem = sd(count, na.rm = T) / sqrt(sum(!is.na(count)))) %>%
  left_join(graph_colors) %>%
  mutate(color = factor(color, levels = colors))
